\begin{thebibliography}{99}

\bibitem{sahli2023load} Sahli, A. y otros. (2023). \textit{Automated Load Testing for RESTful APIs: A Comparative Study}. 2023 International Conference on Software Engineering and Knowledge Engineering.

\bibitem{vukovic2020performance} Vuković, M. y otros. (2020). \textit{Performance testing of web services: A comparison of JMeter and k6}. IEEE 43rd International Convention on Information, Communication and Electronic Technology (MIPRO), pp. 1122--1127. doi: \url{https://doi.org/10.23919/MIPRO48933.2020.9245131}

\bibitem{bezemer2019performance} Bezemer, C. P. y otros. (2019). \textit{Performance Challenges in Microservices and Proposed Solutions}. Communications of the ACM, 62(10), 68--77. doi: \url{https://doi.org/10.1145/3338119}

\bibitem{chucksacademyPerformance} Pruebas de Carga y Rendimiento. (2025). Recuperado de \url{https://www.chucksacademy.com/es/topic/node-testing-jest/load-performance-testing}. Accedido en 2025.

\bibitem{turn0search1} Métricas de Load Testing. (2025). Documento académico en Scribd sobre pruebas de rendimiento. Accedido en 2025.

\bibitem{turn0search5} K6 Performance Test Starter. (2025). Recuperado de \url{https://github.com/Automation-Test-Starter/K6-Performance-Test-starter}. Accedido en 2025.

\bibitem{turn0search9} Performance Testing from Beginner to Expert with k6. (2025). Recuperado de \url{https://medium.com/@sanil.dsilva_70965/performance-testing-from-beginner-to-expert-with-k6-a324d0809d40}. Accedido en 2025.

\bibitem{nodejsorg2024} Node.js. (2024). \textit{Node.js}. Recuperado de \url{https://nodejs.org/en}. Accedido en 2025.

\bibitem{expressjs2024} Express - Node.js web application framework. (2024). Recuperado de \url{https://expressjs.com/}. Accedido en 2025.

\end{thebibliography}
